Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-02-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\begin{abstract} 
We examine the flow instabilities, \ie viscous fingering on the displacement of one fluid by a second, using a novel computational method for modeling multi-phase flows in heterogeneous porous media. Those "fingers" will multiply and develop further into complex networks that will eventually effect the efficiency of field operations.

Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, the finger development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined. A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions. Finally, a 3D domain setup is showcasing the difference between the preferential flow path and the fingering regimes that will occur in the domain.

@@

\medskip
In the next section \ref{section:results_setup} is an introduction to the model that will be used followed by section \ref{section:results_initial_model_validation} will be discussed. Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}). \red{KOSTAS, please read and rewrite this paragraph!}

>>>>

\begin{abstract} 
We examine flow instabilities that leads to formation and growth of viscous fingers during fluid displacement using a novel computational multi-phase flows model in heterogeneous porous media. Fingers often grow and develop into complex networks that have strong impact on the efficiency of oil and gas exploration.

Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined. A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions. Finally, a 3D domain setup is showcasing the difference between the preferential flow path and the fingering regimes that will occur in the domain.

@@

\medskip
In the next section \ref{section:results_setup} is an introduction to the model that will be used followed by section \ref{section:results_initial_model_validation} will be discussed. Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).
